Use and acquisition of causal relations for decision making under uncertainty using imperfect information games

### 2020-09-01 3rd_year_eval/Slides/3rd_year_slides.tex
slides 5 6 7 en una sola

\begin{frame}
\tableofcontents
\end{frame}

\section{Introduction and Problem Statement}
\begin{frame}
\begin{center}
\LARGE{Introduction}
\end{center}
\end{frame}
\subsection{Introduction}
\begin{frame}
\frametitle{Main idea}
How to learn and use causal information in order to make a good choice in an uncertain environment?
\end{frame}

\begin{frame}
\frametitle{Two components}
We notice two components from the main idea:
\begin{itemize}
\item Learn.
\item Use.
\end{itemize}
\end{frame}

\begin{frame}
Previously we focused on the \textit{use} part.
\end{frame}

\subsection{Relevance}
\begin{frame}
\frametitle{Why?}
\begin{itemize}
\item Decision Making Under uncertainty (DMU) is fundamental for Artificial Intelligence (\cite{lake2017building}).
\item Any Bayesian procedure is based on Decision Making
\item Optimal policies in Reinforcement Learning are the \textit{best} action for each state.
\item Reinforcement Learning (RL) is \textit{not} a Causal Problem.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Why?}
\begin{itemize}
\item Mainstream ideas in DMU work at the \textit{associative}\footnote{probabilities, correlations...} level of information.
\item In fact, Optimal Policies in RL satisfy the classical criterion of Maximum Expected Utility.
\item Given the importance of Causation in science \textbf{we consider decision making theory that relies on causal information.}
\end{itemize}
\end{frame}

@@

\subsection{Bayesian Non parametrics}
\begin{frame}
\frametitle{Future Work: Bayesian Nonparametrics}
Bayesian non parametrics is a field within Bayesian statistics in which priors of infinite dimension are allowed, so models with a greater expressibility can be developed.
\begin{itemize}
\item Priors over complex graphs.
\item Fully Bayesian learning procedure.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
\item This year we have focused on learning an unknown \textit{causal structure} by interacting with a causally controlled environment.
\item Previously, we had addressed the question on how to \textit{use} causal information in order to make good choices. 
\item Together, this two tasks answer questions 1, 2 and 3 of the mentioned Research Questions.
\end{itemize}
\end{frame}

>>>>

\begin{frame}[allowframebreaks]
\tableofcontents
\end{frame}

\section{Introduction and Problem Statement}
\begin{frame}
\begin{center}
\LARGE{Introduction}
\end{center}
\end{frame}
\subsection{Introduction}
\begin{frame}
\frametitle{Main idea}
\begin{itemize}
\item How to learn and use causal information in order to make a good choice in an uncertain environment?
\item We notice two components from the main idea:
	\begin{enumerate}
		\item Learn
		\item Use
	\end{enumerate}
\end{itemize}
Previously we focused on the \textit{use} part.
\end{frame}

\subsection{Relevance}
\begin{frame}
\frametitle{Why?}
\begin{itemize}
\item Decision Making Under uncertainty (DMU) is fundamental for Artificial Intelligence (\cite{lake2017building}).
\item Any Bayesian procedure is based on Decision Making
\item Optimal policies in Reinforcement Learning are the \textit{best} action for each state.
\item Reinforcement Learning (RL) is \textit{not} a Causal Problem \citep{gonzalez2019reinforcement}.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Why?}
\begin{itemize}
\item Mainstream ideas in DMU work at the \textit{associative} level of information.
\item In fact, Optimal Policies in RL satisfy the classical criterion of Maximum Expected Utility \citep{webb2007game}.
\item Given the importance of Causation in science \textbf{we consider decision making theory that relies on causal information.}
\end{itemize}
\end{frame}

@@

\subsection{Bayesian Non parametrics}
\begin{frame}
\frametitle{Future Work: Bayesian Nonparametrics}
Bayesian non parametrics is a field within Bayesian statistics in which priors of infinite dimension are allowed, so models with a greater expressibility can be developed.
\begin{itemize}
\item Priors over complex graphs.
\item Fully Bayesian learning procedure.
\end{itemize}
Using a Bayesian Nonparametric prior we could define probabilities over a space of \textit{graphs} and automate what we have done here.
\end{frame}

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
\item This year we have focused on learning an unknown \textit{causal structure} by interacting with a causally controlled environment.
\item Previously, we had addressed the question on how to \textit{use} causal information in order to make good choices. 
\item We extended the \textit{use} part to a multi-agent setting; Causal Games.
\item Together, this two tasks answer questions 1, 2 and 3 of the mentioned Research Questions.
\end{itemize}
\end{frame}
